CS-B Tandem Deamination Figure Generation

### 2022-06-13 R/CS-BTandemDeaminationFigureGeneration.rmd
Refactored tandem deamination directory names
Refactored tandem deamination directory names to accompany directory changes which put tandem deamination data back into the same directories as other mismatch data.

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in seq_along(CPDMismatchData)) {
  for (j in seq_along(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMismatchData)) {
  for (j in seq_along(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

@@

```{r read_mismatch_frequency_z-score_tables}
CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDMMFreqZScores)) {
  for (j in seq_along(CPDMMFreqZScores[[i]])) {
    CPDMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMMFreqZScores)) {
  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

@@

```{r read_mismatch_position_statistics}
CPDGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                       rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(CPDGroupedStats)) {
  for (j in seq_along(CPDGroupedStats[[i]])) {
    CPDGroupedStats[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
      strandPolarity = names(CPDGroupedStats[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

sixFourGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                           rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(sixFourGroupedStats)) {
  for (j in seq_along(sixFourGroupedStats[[i]])) {
    sixFourGroupedStats[[i]][[j]] = fread(generateFilePath(
      tandemDeaminationDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
      strandPolarity = names(sixFourGroupedStats[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

@@

```{r read_nucleotide_frequency_data}
threePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
  threePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

fivePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  fivePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

threePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
  threePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

fivePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
  fivePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
    directory = tandemDeaminationDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}
```

@@

```{r read_sequence_frequency_data}
threePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
                                      rep2 = CPDTimepoints)
for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCPDSeqFreq[[i]])) {
    threePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

fivePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
                                     rep2 = CPDTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCPDSeqFreq[[i]])) {
    fivePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

threePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints,
                                          rep2 = sixFourTimepoints)
for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredSixFourSeqFreq[[i]])) {
    threePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

fivePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints,
                                         rep2 = sixFourTimepoints)
for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredSixFourSeqFreq[[i]])) {
    fivePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = tandemDeaminationDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

>>>>

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
CPDMismatchData = list(rep1 = CPDTimepoints,
                       rep2 = CPDTimepoints)
for (i in seq_along(CPDMismatchData)) {
  for (j in seq_along(CPDMismatchData[[i]])) {
    CPDMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "CPD", timepoint = names(CPDMismatchData[[i]])[j],
      repitition = names(CPDMismatchData)[i], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

sixFourMismatchData = list(rep1 = sixFourTimepoints,
                           rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMismatchData)) {
  for (j in seq_along(sixFourMismatchData[[i]])) {
    sixFourMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "6-4", timepoint = names(sixFourMismatchData[[i]])[j],
      repitition = names(sixFourMismatchData)[i], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

@@

```{r read_mismatch_frequency_z-score_tables}
CPDMMFreqZScores = list(rep1 = CPDTimepoints, rep2 = CPDTimepoints)
for (i in seq_along(CPDMMFreqZScores)) {
  for (j in seq_along(CPDMMFreqZScores[[i]])) {
    CPDMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDMMFreqZScores)[i],
      timepoint = names(CPDMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

sixFourMMFreqZScores = list(rep1 = sixFourTimepoints, rep2 = sixFourTimepoints)
for (i in seq_along(sixFourMMFreqZScores)) {
  for (j in seq_along(sixFourMMFreqZScores[[i]])) {
    sixFourMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourMMFreqZScores)[i],
      timepoint = names(sixFourMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

@@

```{r read_mismatch_position_statistics}
CPDGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                       rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(CPDGroupedStats)) {
  for (j in seq_along(CPDGroupedStats[[i]])) {
    CPDGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(CPDGroupedStats)[i],
      strandPolarity = names(CPDGroupedStats[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

sixFourGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                           rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(sixFourGroupedStats)) {
  for (j in seq_along(sixFourGroupedStats[[i]])) {
    sixFourGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(sixFourGroupedStats)[i],
      strandPolarity = names(sixFourGroupedStats[[i]])[j], filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```

@@

```{r read_nucleotide_frequency_data}
threePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
  threePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

fivePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  fivePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

threePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
  threePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}

fivePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
  fivePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering, includedMismatches = mismatchType
  ))
}
```

@@

```{r read_sequence_frequency_data}
threePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
                                      rep2 = CPDTimepoints)
for (i in seq_along(threePrimeMMAnchoredCPDSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredCPDSeqFreq[[i]])) {
    threePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

fivePrimeMMAnchoredCPDSeqFreq = list(rep1 = CPDTimepoints,
                                     rep2 = CPDTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCPDSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredCPDSeqFreq[[i]])) {
    fivePrimeMMAnchoredCPDSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredCPDSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

threePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints,
                                          rep2 = sixFourTimepoints)
for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
  for (j in seq_along(threePrimeMMAnchoredSixFourSeqFreq[[i]])) {
    threePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourSeqFreq)[i],
      timepoint = names(threePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}

fivePrimeMMAnchoredSixFourSeqFreq = list(rep1 = sixFourTimepoints,
                                         rep2 = sixFourTimepoints)
for (i in seq_along(fivePrimeMMAnchoredSixFourSeqFreq)) {
  for (j in seq_along(fivePrimeMMAnchoredSixFourSeqFreq[[i]])) {
    fivePrimeMMAnchoredSixFourSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourSeqFreq)[i],
      timepoint = names(fivePrimeMMAnchoredSixFourSeqFreq[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering, includedMismatches = mismatchType
    ))
  }
}
```
